Name matching through deep learning

### 2018-12-02 old/paper2018/evaluation.tex
fixed a set of typos and errors

\section{Experiments}
\label{results}
In building the models, we employed early stopping using the usual metric of accuracy of the validation data, and we performed hyper-parameter tuning using grid search varying margins for the adapted loss function from 1-20.  Accuracy was defined as the percentage of validation triples where positive distances from anchor were less than negative distances from anchor.  For all our runs, test accuracy as measured by this metric ranged in the 97-98\% range for the people dataset and 99\% companies dataset for all losses except angular loss which was poor throughout.  Table \ref{precision_recall} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.  Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.  For all the results reported here, we ran multiple runs because of the stochastic nature of neural network models; the results here are for the better of the two runs.

@@

\subsection{Performance for Joins}
For fuzzy joins, we need both precision and recall to be high.  Without good recall, a join will potentially miss names that should be joined.  Without high precision, a join will mistakenly join many inappropriate names.  The best numbers across the models were 82\% for people and 76\% for companies, so a join could capture most similar names.  For people, the adapted loss function showed overall better performance than triplet loss (see Table \ref{precision_recall}).  Furthermore, it appears that triplet loss outperformed improved loss, which in turn is better than angular loss for learning this problem.  On the other hand, for companies, triplet loss seemed the best, which suggests that the properties of the dataset combine with loss functions to influence performance.

@@

We therefore compared the hard negative triplet selection mechanism directly to training against semi-hard negatives.  To compute semi-hard negatives, we took, for each entity, all its positives, and found all negatives in the nearest neighborhood of that positive that were further from the entity than is the positive.  We made triplets for each such pair of positive and negative.  We thus chose the hardest semi-hard triplets: the negatives are as close to the positive as possible while still being further from the entity.  We ran experiments again for adapted loss on our people dataset, changing only the triplets used; these results are in Figure~\ref{hard-semi-hard}.  The same comparison on the company dataset showed no difference, mostly because company data seems easier and seems more immune to differences in loss functions or training regimens.

@@

\section{Conclusion and Future Work}
We show that deep learning models can be used effectively for joins, and we provide these models to the community for use.  In the future, we will evaluate our work on other entity types and continue to explore refinements of both loss functions and triplet selection.

>>>>

\section{Experiments}
\label{results}
In building the models, we employed early stopping using the usual metric of accuracy of the validation data, and we performed hyper-parameter tuning using grid search varying margins for the adapted loss function from 1-20.  Accuracy was defined as the percentage of validation triples where positive distances from anchor were less than negative distances from anchor.  For all our runs, test accuracy as measured by this metric ranged in the 97-98\% range for the people dataset and 99\% companies dataset for all losses except angular loss which was poor throughout.  Figure \ref{training-impact} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.  Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.  For all the results reported here, we ran multiple runs because of the stochastic nature of neural network models; the results here are for the better of the two runs.

@@

\subsection{Performance for Joins}
For fuzzy joins, we need both precision and recall to be high.  Without good recall, a join will potentially miss names that should be joined.  Without high precision, a join will mistakenly join many inappropriate names.  The best recall across the models were 79\% for people and 74\% for companies, so a join could capture most similar names.  For people, the adapted loss function showed overall better performance across precision and recall than triplet loss (see Figure \ref{precision_recall}).  Furthermore, it appears that triplet loss outperformed improved loss, which in turn is better than angular loss for learning this problem.  On the other hand, for companies, triplet loss seemed the best, which suggests that the properties of the dataset combine with loss functions to influence performance.

@@

We therefore compared the hard negative triplet selection mechanism directly to training against semi-hard negatives.  To compute semi-hard negatives, we took, for each entity, all its positives, and found all negatives in the nearest neighborhood of that positive that were further from the entity than is the positive.  We made triplets for each such pair of positive and negative.  We thus chose the hardest semi-hard triplets: the negatives are as close to the positive as possible while still being further from the entity.  We ran experiments again for adapted loss on our people dataset, changing only the triplets used; these results are in Figure~\ref{hard-semi-hard}.  The same comparison on the company dataset showed no difference, mostly because company data seems easier and seems more robust to differences in loss functions or training regimens.

@@

\section{Conclusion and Future Work}
We show that deep learning models can be used effectively for joins, and we provide these models to the community for use.  This suggests that deep learning can be applied for matching other surface forms of entities such as addresses or product names.  Future extensions to this work is how to use these models in the problem of entity matching, where each database often has different attributes for the same entity.

### 2018-12-02 old/paper2018/introduction2.tex
fixed a set of typos and errors

We propose a different approach to joining different surface representations of the same entity, inspired by recent advances in deep learning: (a) map surface forms into sets of vectors such that forms for the same entity are closest in vector space, (b) index these vectors to find the forms that can be potentially joined together.  Once a model has been built for a specific semantic type (e.g. people, companies or faces) it can be used for joining any two datasets which share that semantic type, provided the sample characteristics match.  It is efficient by using space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable.  Nearest neighbor algorithms have been applied to billions of vectors \cite{JDH17}, so the approach is practical for most datasets.

We evaluate using Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).  The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning (e.g. \cite{DBLP:conf/cvpr/SchroffKP15}), and there is research on two aspects of training these networks: (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.  In building models for entity names, we adapt these techniques for triplet selection and loss functions because matching entity names has different characteristics.

As in face recognition, we use a triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen \textit{anchor} and \textit{positive}), and a large distance estimate for surface forms of different entities (an \textit{anchor} and a \textit{negative}).  A key problem in effective training of such networks is how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.  In prior work for instance, this done by finding `semi-hard' negatives after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.  `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.  The idea of focusing on semi-hard negatives is to avoid mining noisy regions of the embedding space.  However, for matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than some negatives, as we show empirically in this paper, so `hard negatives' dominate the space.  We therefore use an approximate nearest neighbors (ANN) algorithm to choose negatives for training that were in the nearest neighbor set, and hence are `hard negatives', being closer to the anchor than positives.  This approach has three benefits.  First, an ANN allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch.  Second, it provides a baseline against which one can objectively measure the effects of training.  Third, it examines whether hard negatives really are detrimental to deep metric learning, at least for learning to map entity names in vector space.  As we show empirically in this paper, this technique is better for building models that are suitable for use in joins than semi-hard triplet mining when the dataset is dominated by hard negatives.  For easier datasets, the nearest neighbors approach was just as good as semi-hard training.

We compared multiple proposed local loss functions---Schroff\cite{DBLP:conf/cvpr/SchroffKP15}, improved\cite{Zhang:2016:DML:3088616.3088665}, and angular\cite{DBLP:journals/corr/abs-1708-01682}---and we found an adaptation of the Schroff loss function worked best.

>>>>

We propose a different approach to joining different surface representations of the same entity, inspired by recent advances in deep learning: (a) map surface forms into sets of vectors such that forms for the same entity are closest in vector space, (b) index these vectors to find the forms that can be potentially joined together.  Once a model has been built for a specific semantic type (e.g. people, companies or faces) it can be used for joining any two datasets which share that semantic type, provided the sample characteristics match.  It can be made efficient by using space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable.  Nearest neighbor algorithms have been applied to billions of vectors \cite{JDH17}, so the approach is practical for most datasets.

We evaluate this approach by using Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).  The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning (e.g. \cite{DBLP:conf/cvpr/SchroffKP15}), and there is research on two aspects of training these networks: (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.  In building models for entity names, we adapt these techniques for triplet selection and loss functions because matching entity names has different characteristics.

As in face recognition, we use a triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen \textit{anchor} and \textit{positive}), and a large distance estimate for surface forms of different entities (an \textit{anchor} and a \textit{negative}).  A key problem in effective training of such networks is how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.  In prior work for instance, this was done by finding `semi-hard' negatives after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.  `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.  The idea of focusing on semi-hard negatives is to avoid mining noisy regions of the embedding space.  However, for matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than some negatives, as we show empirically in this paper, so `hard negatives' dominate the space.  We therefore use an approximate nearest neighbors (ANN) algorithm to choose negatives for training that were in the nearest neighbor set, and hence are `hard negatives', being closer to the anchor than positives.  This approach has three benefits.  First, an ANN allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch.  Second, it provides a baseline against which one can objectively measure the effects of training.  Third, it examines whether hard negatives really are detrimental to deep metric learning, at least for learning to map entity names in vector space.  As we show empirically in this paper, this technique is better for building models that are suitable for use in joins than semi-hard triplet mining when the dataset is dominated by hard negatives.  For easier datasets, the nearest neighbors approach was just as good as semi-hard training.

We compared also compared multiple proposed local loss functions: triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} along with an adaptation of the triplet loss function for both sorts of datasets.  The main finding here was that the effectiveness of the loss function varied by dataset.  For the harder problem of learning people's names, an adaptation of triplet loss worked best, whereas for easier problem of company names learning, Schroff produced the best learning.

### 2018-12-02 old/paper2018/relatedWork.tex
fixed a set of typos and errors

\section{Related Work}
Extensions in data management systems for joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF; e.g., \cite{Cohen2003}.  String matching algorithms work poorly for merging the same entity because valid transformations of entity names can yield very different strings.  More recently, data driven approaches mine patterns to determine the `rules' for joining a given entity type.  One example is \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.  Another example is\cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.  Our approach for merging datasets is more general because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be directly expressed as program transforms.

>>>>

\section{Related Work}
Extensions in data management systems for joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF; e.g., \cite{Cohen2003}.  String matching algorithms work poorly for merging the same entity because valid transformations of entity names can yield very different strings.  More recently, data driven approaches mine patterns to determine the `rules' for joining a given entity type.  One example is \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.  Another example is \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.  Our approach for merging datasets is more general because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be directly expressed as program transforms.
